---
title: "R Notebook"
author: Peter-NB
date: 11.06.2020
output: html_notebook
---


Preprocessing:
```{r}
if (!exists("paper_amount_month"))
  source("scripts/analyse_papers.R")

```

Each month around 400-800 papers are being published in the Field of
```{r}
papers_statistics <- ggplot(paper_amount_month, aes(x = year_month, y = n)) +
  geom_col(position = "stack")
papers_statistics
```
Analysing all papers published in the period of observation, here you see the proportion of papers that do contain python code, are empty or do contain only the readme file.
```{r}
barify_general <- function(df) {
  result <- df %>%
    group_by(has_py_repo, all_repos_empty, all_repos_readme_only) %>%
    summarise(n = sum(n)) %>%
    spread(has_py_repo, n) %>%
    rename(py_repo = "TRUE", no_py_repo = "FALSE") %>%
    spread(all_repos_empty, no_py_repo) %>%
    rename(empty = "TRUE", not_empty = "FALSE") %>%
    spread(all_repos_readme_only, not_empty) %>%
    rename(readme_only = "TRUE", not_readme_only = "FALSE") %>%
    mutate_all(function(x) if_else(is.na(x), 0, as.double(x))) %>%
    summarise_all(function(x) sum(x)) %>%
    rename(no_py_repo = not_readme_only) %>%
    melt() %>%
    mutate(type = "all_papers")

  result$variable <- factor(result$variable, levels = (c("empty", "readme_only", "no_py_repo", "py_repo")))
  return(result)
}
py_code_all <- barify_general(paper_amount_month)
py_code_mentioned <- barify_general(paper_amount_month_mentioned_paper)

py_code_all$variable <- factor(py_code_all$variable, levels = (c("empty", "readme_only", "no_py_repo", "py_repo")))

ggplot(py_code_all, aes(x = type, y = value, fill = variable)) +
  geom_bar(position = position_stack(), stat = "identity", color = "black") +
  scale_fill_manual(values = c("#872004", "#e03b22", "#d96250", "#60d950"))

ggplot(py_code_mentioned %>% mutate(type = "Mentioned in paper"), aes(x = type, y = value, fill = variable)) +
  geom_bar(position = position_stack(), stat = "identity", color = "black") +
  scale_fill_manual(values = c("#872004", "#e03b22", "#d96250", "#60d950"))
```
How many papers are  connected to more than one repo?
```{r}
paper_repo_analysed %>%
  group_by(paper_url) %>%
  count() %>%
  mutate(more_than_one = n > 1) %>%
  group_by(more_than_one) %>%
  count() %>%
  ungroup()
```

```{r}
#repo_plotable <- repo_stats %>%
#  ungroup() %>%
#  summarise_at(vars(has_py_file, only_readme), function(x) sum(x)) %>%
#  rbind(colnames(.), .) %>%
#  t() %>%
#  as_tibble() %>%
#  rename(n = V2, type = V1) %>%
#  rbind(c("total", repos %>% nrow()))
#
#
#ggplot(repo_plotable, aes(x = type, y = n)) +
#  geom_col()
```

How is the needed environment defined?
```{r}
barify_env <- function(df) {
  result <- df %>%
    select(repo_name, paper_url, date, mentioned_in_github, mentioned_in_paper, commands_rm[3], file_regexes[3], file_regexes[4]) %>%
    mutate(requ_env_setup = .[[7]] > 0, docker_file = .[[8]] > 0, pip = .[[6]] > 0) %>%
    group_by(paper_url) %>%
    mutate(requ_env_setup = any(requ_env_setup), docker_file = any(docker_file), pip = any(pip)) %>%
    filter(row_number() == 1) %>%
    mutate(only_docker = docker_file & !requ_env_setup, only_req = requ_env_setup & !docker_file,
           docker_and_requ = docker_file & requ_env_setup, only_pip = pip & (docker_file & requ_env_setup), not_gl_conform = !(docker_file | requ_env_setup)) %>%
    group_by(only_pip, only_docker, only_req, docker_and_requ, not_gl_conform) %>%
    count() %>%
    # now i try to get thos distjunct sets in one line.
    spread(only_pip, n) %>%
    rename(only_pip = "TRUE", no_only_pip = "FALSE") %>%
    spread(only_req, no_only_pip) %>%
    rename(only_req = "TRUE", no_only_req = "FALSE") %>%
    spread(only_docker, no_only_req) %>%
    rename(only_docker = "TRUE", no_only_docker = "FALSE") %>%
    spread(docker_and_requ, no_only_docker) %>%
    rename(docker_and_requ = "TRUE", no_docker_and_requ = "FALSE") %>%
    spread(not_gl_conform, no_docker_and_requ) %>%
    rename(not_gl_conform = "TRUE", no_not_gl_conform = "FALSE") %>%
    select(-no_not_gl_conform) %>%
    mutate_all(function(x) if_else(is.na(x), 0, as.double(x))) %>%
    summarise_all(function(x) sum(x)) %>%
    melt(value.name = "papers", variable = "environment-specification") %>%
    mutate(type = "all_papers")

  result$`environment-specification` <- factor(result$`environment-specification`, levels = (c("not_gl_conform", "only_pip", "only_req", "only_docker", "docker_and_requ")))
  return(result)
}
plot_bar_env <- function(df) {
  ggplot(df, aes(x = type, y = papers, fill = `environment-specification`)) +
    geom_bar(position = position_stack(), stat = "identity", color = "black") +
    scale_fill_manual(values = c("#872004", "#e03b22", "#63e686", "#60d950", "#32a852"),
                      labels = c("No dependencies", "Only pip comments in README.md", "Only requeriments.txt \nor setup.py or environment.yml", "Only dockerfile", "Dockerfile and requeriments.txt\n or setup.py or environment.yml")) +
    theme(axis.text.x = element_blank())
}
environment <- barify_env(low_gl_satisfactory)
environment_mentioned_paper <- barify_env(low_gl_satisfactory)

plot_bar_env(environment)
plot_bar_env(environment_mentioned_paper)


```
How many paper's repos that have the term "trained model" in their readme do refer to hosting services?
```{r}
bar_refer_hosting <- papers_refer_hosting %>%
  group_by(one_repo_refers_to_hosting_page) %>%
  count() %>%
  melt()

ggplot(bar_refer_hosting, aes(x = variable, y = value, fill = one_repo_refers_to_hosting_page)) +
  geom_bar(position = position_stack(), stat = "identity", color = "black") +
  scale_fill_manual(values = c("#872004", "#60d950"),
                    labels = c("No", "Yes")) +
  theme(axis.text.x = element_blank()) +
  guides(fill = guide_legend(title = "Is at least one repo connected\n to paper refering to hosting site?"))
```

```{r}
barify_train_eval <- function(df) {
  result <- df %>%
    group_by(train_sat, eval_sat) %>%
    count() %>%
    mutate(type = "all_papers", variable = case_when(train_sat & !eval_sat ~ "train but no eval",
                                                     eval_sat & !train_sat ~ "eval but no train",
                                                     eval_sat & train_sat ~ "eval and train",
                                                     !eval_sat & !train_sat ~ "not eval nor train",
                                                     TRUE ~ "")) %>%
    select(-train_sat, -eval_sat)

  result$variable <- factor(result$variable, levels = c("not eval nor train", "eval but no train", "train but no eval", "eval and train"))
  return(result)
}
plot_bar_eval_train <- function(df) {
  ggplot(df, aes(x = type, y = n, fill = variable)) +
    geom_bar(position = position_stack(), stat = "identity", color = "black") +
    scale_fill_manual(values = c("#872004", "#db8f14", "#fade0f", "#60d950")) +
    guides(fill = guide_legend(title = ""))
}

overall_train_eval <- barify_train_eval(low_gl_satisfactory)
train_eval_mentioned_paper <- barify_train_eval(low_gl_satisfactory %>% filter(mentioned_in_paper == 1))

plot_bar_eval_train(overall_train_eval)
plot_bar_eval_train(train_eval_mentioned_paper)

```


```{r}
low_gl_plotable <- low_gl_satisfactory %>%
  mutate(year_month = floor_date(ymd(date), "month")) %>%
  group_by(year_month) %>%
  summarise_at(vars(c("train_sat", "eval_sat", "req_sat", "full_sat")), function(x) sum(x) / n())

library(RColorBrewer)
low_time_rm_sat_plot <- ggplot(low_gl_plotable, aes(x = year_month, y = 1)) +
  geom_line(aes(x = year_month, y = train_sat, color = "Train")) +
  geom_line(aes(x = year_month, y = eval_sat, color = "Eval")) +
  geom_line(aes(x = year_month, y = req_sat, color = "Dependencies")) +
  geom_line(aes(x = year_month, y = full_sat, color = "All")) +
        labs(color='Papers satisfying:')
low_time_rm_sat_plot


```
```{r}
full_sat_all_papers <- low_gl_satisfactory %>%
        group_by(paper_url) %>%
        mutate(full_sat_all_repos = any(full_sat)) %>%
        filter(row_number()==1) %>%
        ungroup() %>%
        count(full_sat_all_repos)
```